### 2009-04-03 talk/icooolps2009-dotnet/clibackend.tex
number each block and refer to them in the explanation

\begin{figure}[h]
\begin{center}
\includegraphics[height=4.5cm]{flexswitch1}
\includegraphics[height=4.5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right a new block has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

In the pictures of Figure~\ref{flexswitch-fig}, the cyan block
corresponds to a flexswitch; initially (picture on the left) 
only the block containing the code to restart the JIT compilation
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking the cyan block with a freshly created new block.

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[height=5cm]{flexswitch1}
\includegraphics[height=5cm]{flexswitch2}
\caption{An example of a flexswitch evolution: in the picture on the
  right a new block has been dynamically added.}\label{flexswitch-fig}
\end{center}
\end{figure}

In the pictures of Figure~\ref{flexswitch-fig}, block 5 (highlighted in grey)
corresponds to a flexswitch; initially (picture on the left) 
only block 5, containing the code to restart the JIT compilation,
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking block 5 with the freshly created block number 7..
